### 2018-11-29 manuscript/manuscript.rmd
parses all matrices

partition_map_global = 
	read_tsv("../reconciliation/blast/graphs/diamond_partition_clusters.tsv") %>%
	dplyr::rename(partition=partition_name) %>%
	dplyr::rename(matrix=dataset)

@@

phylip_file_names = list.files(pattern = "blast/phylips/.+\\.phy$")

a_file = "../data_processed/matrices/Chang2015_Chang2015.phy"
p_file = "../data_processed/matrices/Chang2015_Chang2015.nex"
msa = PartitionedMultipleAlignment( a_file, p_file, taxa, partition_map_global=partition_map_global, manuscript_name="Chang2015", matrix_name="Chang2015")

D=clade_rects(msa)

>>>>

partition_map_global = 
	read_tsv("../reconciliation/blast/graphs/diamond_partition_clusters.tsv") %>%
	dplyr::rename(partition=partition_name) %>%
	dplyr::rename(matrix=dataset) %>% 
	dplyr::rename(gene=cluster_number)

@@

matrix_path = "../data_processed/matrices/"
phylip_file_names = list.files(path = matrix_path, pattern = ".+\\.phy$")

msas = lapply(
	phylip_file_names,
	function( phylip_file ){
		print(phylip_file)
		partition_file = sub( "phy$", "nex", phylip_file )

		phylip_path = paste(c(matrix_path, phylip_file), collapse="")
		partition_path = paste(c(matrix_path, partition_file), collapse="")

		base_name = sub( "\\.phy$", "", phylip_file )
		elements = strsplit(base_name, "_") %>% unlist()
		manuscript_name = elements[1]
		matrix_name = paste(elements[2:length(elements)], collapse="_")

		msa = 
			PartitionedMultipleAlignment( 
				phylip_path, 
				partition_path, 
				taxa, 
				partition_map_global=partition_map_global, 
				manuscript_name=manuscript_name, 
				matrix_name=matrix_name
			)

		return( msa )
	}
)

a_file = "../data_processed/matrices/Chang2015_Chang2015.phy"
p_file = "../data_processed/matrices/Chang2015_Chang2015.nex"
msa = 
	PartitionedMultipleAlignment( 
		a_file, 
		p_file, 
		taxa, 
		partition_map_global=partition_map_global, 
		manuscript_name="Chang2015", 
		matrix_name="Chang2015"
	)

D=clade_rects(msas[[1]])
